Fast, Scalable Phrase-Based SMT Decoding

### 2016-01-28 acl.2016/acl2016.tex
acl paper

However, we also note that distortion limit which constrains hypothesis extension is dependent on the hypothesis' coverage vector \emph{and} the end position of most recent source word that has been translated. Using a cardinality-based stack, the distortion limit must be checked for every instance, Figure~\ref{algo:Hypothesis Expansion with Unsorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\STATE insert empty hypothesis into $stack_0$
\FOR{$i = 0$ to $|s|-1$} 
  \STATE prune $stack_i$
  \FORALL{ hypothesis in $stack_i$} 
    \FORALL{ translation options}
       \IF {hypothesis and translation option are compatible}
         \STATE expand hypothesis with translation option $\rightarrow$ new hypothesis
         \STATE coverage of  new hypothesis $\rightarrow C$
         \STATE insert new hypothesis $\rightarrow stack_{|C|}$
         \STATE recombine new hypothesis if possible
         \STATE prune $stack_{|C|}$ if necessary
       \ENDIF
    \ENDFOR % { translation options}
  \ENDFOR % { hypothesis in $stack_i$} 
\ENDFOR% {$i = 0$ to $|s|-1$} 
\RETURN highest scoring hypothesis in $stack_{|s|}$
\end{algorithmic}
\caption{Hypothesis Expansion with Unsorted Stack}
\label{algo:Hypothesis Expansion with Unsorted Stack}
\end{figure}

Therefore, if the hypotheses are separated by coverage vector and end position, the distortion limit constraint can be moved to an outer loop, potentially speeding up decoding.

>>>>

We also note that distortion limit which constrains hypothesis extension is dependent on the hypothesis' coverage vector \emph{and} the end position of most recent source word that has been translated. The distortion limit must be checked for every instance of a hypothesis and translation rule, Figure~\ref{algo:Hypothesis Expansion with Unsorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\FORALL{ hypo in $stack$} 
  \FORALL{ translation rules}
      \IF {CanExpand(hypo coverage, hypo end position, translation rule range)}
	\STATE expand hypo with translation rule $\rightarrow$ new hypo
	\STATE add new hypo into next stack
      \ENDIF
  \ENDFOR % { translation options}
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Hypothesis Expansion with Unsorted Stack}
\label{algo:Hypothesis Expansion with Unsorted Stack}
\end{figure}
However, by separating hypotheses according to coverage and end position, the distortion limit check only needs to be done for each stack, potentially speeding up decoding, Figure~\ref{algo:Hypothesis Expansion with Sorted Stack}.
\begin{figure} [h]
\begin{algorithmic}
%\REQUIRE source sentence $s$, translation options
\FORALL{ coverage and end position in $stack$}
  \FORALL{ translation rules}
      \IF {CanExpand(coverage, end position, translation rule range)}
        \FORALL{hypo in [coverage and end position]}
  	  \STATE expand hypo with translation rule $\rightarrow$ new hypo
	  \STATE add new hypo into $next stack$
	\ENDFOR
      \ENDIF
  \ENDFOR % { translation options}
\ENDFOR % { hypothesis in $stack_i$} 
\end{algorithmic}
\caption{Hypothesis Expansion with Sorted Stack}
\label{algo:Hypothesis Expansion with Sorted Stack}
\end{figure}
